Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-01 manuscript.Rmd
Small multiples working.

```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")
hIndex$h5Index <- ifelse(is.na(hIndex$h5Index), 0, hIndex$h5Index)
hIndex$h5Median <- ifelse(is.na(hIndex$h5Median), 0, hIndex$h5Median)

@@

```{r dataNSF, eval=TRUE}
n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
    308, 289, 280, NA)

years <- c(1989:2013)

nsf <- data.frame(cbind(n.grads,  years))
colnames(nsf) <- c("n.grads", "years")
```

@@

```{r plotSmallMultiples}
hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
hIndex.df$top10 <- NA
hIndex.df$top10[1:10] <- "yes"
hIndex.df$top10[11:nrow(hIndex.df)] <- "no"
hIndex.df <- data.frame(hIndex.df)

sm.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title)

sm.df <- full_join(sm.df, hIndex.df, by = "title") %>% 
    ungroup %>% 
    select(-h5Median)

sm.df$top10 <- ifelse(is.na(sm.df$top10), "no", sm.df$top10)

title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)

title.order <- title$title

sm.df$title2 <- factor(sm.df$title, levels = (title.order))

Overall.N <- distinct(sm.df, title)

x.df <- data.frame(title = Overall.N$title, label = title$Overall.N)

xpos = rep(10, 78)
ypos = rep(130, 78)
lab <- Overall.N$Overall.N
title2 <- unique(sm.df$title2)

ldata <- data.frame(xpos, ypos, lab, title2)

ggplot(sm.df, aes(year, N, group = 1)) + geom_line(aes(colour = top10)) + 
facet_wrap( ~ title2, ncol=7) +
theme_bw() +
theme(panel.grid.major = element_blank(), 
panel.grid.minor = element_blank(), 
axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
ylim(0, 150) + 
geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab, size =1), parse=FALSE)

>>>>

```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

@@

```{r plotSmallMultiples}

# Create an initial data frame from HD
sm.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title) %>%
    rename(Year = year, Journal= title)

# Read Scopus database
scopus.df <- read.csv("scopus.csv")

# Join HD with Scopus and join abbreviation names
sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
    select(Year, Journal, N, Overall.N, Documents)

abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
abb$ID <- 1:nrow(abb)
sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
    select(-X) %>%
    mutate(Documents = ifelse(Documents == 0, NA, Documents))

# Re-order the factor by Overall.N
title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
    distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()

title.order = title$Abbrev

sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))

# Create labels for the facets
Overall.N <- distinct(sm.scopus.merged, Abbrev) 
lab <- paste("N=", Overall.N$Overall.N, sep="")
xpos = rep(2002, 79)
ypos = rep(215, 79)
ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
    rename(Abbrev = Overall.N.Abbrev)

# Plotting function    
ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99") + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
    ylim(c(0,225)) +
    scale_x_continuous(breaks=seq(1989, 2020, 8))
